Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2021-11-30 s675/rdpg.Rmd
doing an r demo for lecture 2 as well

* $A = V \Lambda V^\top$
* $\hat{X} = V_{p,q} |\Lambda_{p,q}|^{1/2}$
  * $V_{p,q} = \begin{bmatrix} V_{1:p} & | & V_{n-q+1:n} \end{bmatrix}$
  * $\Lambda_{p,q} = \diag(\lambda_1, ..., \lambda_p, \lambda_{n-q+1}, ..., \lambda_n)$
* Not unique
  * If $\hat{X}$ is a solution, then so is $\hat{X} Q$
* $\max_i \|\hat{x}_i - Q x_i \| \stackrel{a.s.}{\to} 0$ (Rubin-Delanchy et al., 2020)

@@

>>>>

* $A = V \Lambda V^\top$
* $\hat{X} = V_{p,q} |\Lambda_{p,q}|^{1/2}$
  * $V_{p,q} = \begin{bmatrix} V_{1:p} \mid V_{n-q+1:n} \end{bmatrix}$
  * $\Lambda_{p,q} = \diag(\lambda_1, ..., \lambda_p, \lambda_{n-q+1}, ..., \lambda_n)$
* Not unique
  * If $\hat{X}$ is a solution, then so is $\hat{X} Q$
* $\max_i \|\hat{x}_i - Q x_i \| \stackrel{a.s.}{\to} 0$ (Rubin-Delanchy et al., 2020)

# R Demo

@@

We can connect block models to the (G)RDPG
